\documentclass[11pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{xcolor}
\usepackage{titlesec}

\pagestyle{fancy}
\fancyhf{}
\rhead{CONFIDENTIAL}
\lhead{Credit Agreement - TechFlow Solutions Inc.}
\rfoot{Page \thepage}

\titleformat{\section}{\large\bfseries}{\thesection.}{0.5em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{0.5em}{}

\begin{document}

\begin{center}
{\LARGE\bfseries CREDIT AGREEMENT}\\[0.5cm]
{\large dated as of January 15, 2024}\\[1cm]
{\Large between}\\[0.5cm]
{\Large\bfseries TECHFLOW SOLUTIONS INC.}\\
{\normalsize (as Borrower)}\\[0.5cm]
{\Large and}\\[0.5cm]
{\Large\bfseries FIRST NATIONAL BANK, N.A.}\\
{\normalsize (as Administrative Agent and Lender)}\\[1cm]
\rule{0.8\textwidth}{0.4pt}\\[0.5cm]
{\large REVOLVING CREDIT FACILITY}\\
{\large \$25,000,000}\\[0.5cm]
\rule{0.8\textwidth}{0.4pt}
\end{center}

\vspace{1cm}

\section{DEFINITIONS AND INTERPRETATION}

\subsection{Defined Terms}
As used in this Agreement, the following terms have the meanings specified below:

\textbf{"Borrower"} means TechFlow Solutions Inc., a Delaware corporation.

\textbf{"Commitment Amount"} means Twenty-Five Million Dollars (\$25,000,000).

\textbf{"EBITDA"} means, for any period, Net Income for such period plus (a) Interest Expense, (b) income tax expense, (c) depreciation expense, and (d) amortization expense, in each case to the extent deducted in determining Net Income.

\textbf{"Interest Coverage Ratio"} means, as of any date of determination, the ratio of (a) EBITDA for the trailing twelve-month period to (b) Interest Expense for such period.

\textbf{"Leverage Ratio"} means, as of any date of determination, the ratio of (a) Total Debt as of such date to (b) EBITDA for the trailing twelve-month period.

\textbf{"Maturity Date"} means January 15, 2029.

\textbf{"Total Debt"} means all indebtedness for borrowed money, including capital leases.

\section{THE CREDIT FACILITY}

\subsection{Revolving Loans}
Subject to the terms and conditions hereof, the Lender agrees to make revolving loans to the Borrower from time to time during the Availability Period in an aggregate principal amount not to exceed the Commitment Amount.

\subsection{Interest Rate}
Each Loan shall bear interest at a rate per annum equal to SOFR plus 2.50\% (the "Applicable Margin").

\subsection{Maturity}
The Loans, together with all accrued and unpaid interest, shall be due and payable on the Maturity Date.

\section{FINANCIAL COVENANTS}

The Borrower covenants and agrees that, so long as any Obligation remains outstanding:

\subsection{Maximum Leverage Ratio}
The Borrower shall not permit the Leverage Ratio, measured as of the last day of each fiscal quarter, to exceed the following:

\begin{center}
\begin{tabular}{|l|c|}
\hline
\textbf{Period} & \textbf{Maximum Ratio} \\
\hline
Closing Date through December 31, 2024 & 4.50:1.00 \\
January 1, 2025 through December 31, 2025 & 4.00:1.00 \\
January 1, 2026 and thereafter & 3.50:1.00 \\
\hline
\end{tabular}
\end{center}

\subsection{Minimum Interest Coverage Ratio}
The Borrower shall not permit the Interest Coverage Ratio, measured as of the last day of each fiscal quarter, to be less than \textbf{2.50:1.00}.

\subsection{Minimum EBITDA}
The Borrower shall not permit EBITDA, measured for the trailing twelve-month period ending on the last day of each fiscal quarter, to be less than \textbf{\$8,000,000}.

\section{REPORTING REQUIREMENTS}

\subsection{Compliance Certificate}
Within 45 days after the end of each fiscal quarter, the Borrower shall deliver to the Administrative Agent a Compliance Certificate signed by the Chief Financial Officer certifying:

\begin{enumerate}
    \item[(a)] Compliance with all financial covenants;
    \item[(b)] Calculation of Leverage Ratio;
    \item[(c)] Calculation of Interest Coverage Ratio;
    \item[(d)] EBITDA for the trailing twelve-month period;
    \item[(e)] Whether any Default or Event of Default exists.
\end{enumerate}

\subsection{Financial Statements}
The Borrower shall deliver:
\begin{enumerate}
    \item[(a)] Within 45 days after each fiscal quarter, unaudited quarterly financial statements;
    \item[(b)] Within 90 days after each fiscal year, audited annual financial statements.
\end{enumerate}

\section{EVENTS OF DEFAULT}

Each of the following shall constitute an Event of Default:

\begin{enumerate}
    \item[(a)] Failure to pay any principal when due;
    \item[(b)] Failure to pay any interest within 5 days of when due;
    \item[(c)] Breach of any financial covenant;
    \item[(d)] Any representation or warranty proving to be false in any material respect;
    \item[(e)] Cross-default on other indebtedness exceeding \$1,000,000.
\end{enumerate}

\section{SIGNATURES}

\vspace{1cm}

\noindent\textbf{BORROWER:}\\[0.5cm]
TECHFLOW SOLUTIONS INC.\\[1cm]
By: \underline{\hspace{5cm}}\\
Name: Michael Chen\\
Title: Chief Executive Officer\\[0.5cm]
Date: January 15, 2024

\vspace{1cm}

\noindent\textbf{LENDER:}\\[0.5cm]
FIRST NATIONAL BANK, N.A.\\[1cm]
By: \underline{\hspace{5cm}}\\
Name: Sarah Williams\\
Title: Senior Vice President\\[0.5cm]
Date: January 15, 2024

\end{document}
