\documentclass[11pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage{fancyhdr}
\usepackage{booktabs}
\usepackage{array}

\pagestyle{fancy}
\fancyhf{}
\rhead{CONFIDENTIAL}
\lhead{Credit Agreement - Midwest Manufacturing Co.}
\rfoot{Page \thepage}

\begin{document}

\begin{center}
{\LARGE\bfseries SENIOR SECURED CREDIT AGREEMENT}\\[0.5cm]
{\large dated as of March 1, 2023}\\[1cm]
{\Large between}\\[0.5cm]
{\Large\bfseries MIDWEST MANUFACTURING CO.}\\
{\normalsize (as Borrower)}\\[0.5cm]
{\Large and}\\[0.5cm]
{\Large\bfseries INDUSTRIAL CREDIT PARTNERS, LLC}\\
{\normalsize (as Administrative Agent and Lender)}\\[1cm]
\rule{0.8\textwidth}{0.4pt}\\[0.5cm]
{\large TERM LOAN FACILITY}\\
{\large \$50,000,000}\\[0.5cm]
\rule{0.8\textwidth}{0.4pt}
\end{center}

\vspace{1cm}

\section{DEFINITIONS}

\textbf{"Borrower"} means Midwest Manufacturing Co., an Ohio corporation.

\textbf{"Commitment Amount"} means Fifty Million Dollars (\$50,000,000).

\textbf{"EBITDA"} means, for any period, Net Income plus (a) Interest Expense, (b) taxes, (c) depreciation, and (d) amortization.

\textbf{"Leverage Ratio"} means Total Debt divided by EBITDA for the trailing twelve months.

\textbf{"Interest Coverage Ratio"} means EBITDA divided by Interest Expense for the trailing twelve months.

\textbf{"Current Ratio"} means Current Assets divided by Current Liabilities.

\textbf{"Maturity Date"} means March 1, 2028.

\section{THE CREDIT FACILITY}

\subsection{Term Loan}
The Lender agrees to make a term loan to the Borrower in the aggregate principal amount of \$50,000,000.

\subsection{Interest Rate}
The Loan shall bear interest at SOFR plus 3.25\%.

\subsection{Amortization}
Principal shall be payable in quarterly installments of \$1,250,000 beginning June 1, 2023.

\section{FINANCIAL COVENANTS}

\subsection{Maximum Leverage Ratio}
The Borrower shall maintain a Leverage Ratio not exceeding:

\begin{center}
\begin{tabular}{|l|c|}
\hline
\textbf{Period} & \textbf{Maximum Ratio} \\
\hline
Through December 31, 2024 & 5.50:1.00 \\
January 1, 2025 through December 31, 2025 & 5.00:1.00 \\
January 1, 2026 and thereafter & 4.50:1.00 \\
\hline
\end{tabular}
\end{center}

\subsection{Minimum Interest Coverage Ratio}
The Borrower shall maintain an Interest Coverage Ratio of not less than \textbf{2.00:1.00}.

\subsection{Minimum Current Ratio}
The Borrower shall maintain a Current Ratio of not less than \textbf{1.25:1.00}.

\subsection{Minimum EBITDA}
The Borrower shall maintain EBITDA of not less than \textbf{\$12,000,000} for any trailing twelve-month period.

\section{REPORTING REQUIREMENTS}

Within 45 days after each fiscal quarter, the Borrower shall deliver a Compliance Certificate certifying compliance with all financial covenants.

\section{EVENTS OF DEFAULT}

The following constitute Events of Default: (a) non-payment, (b) covenant breach, (c) cross-default, (d) bankruptcy, (e) material adverse change.

\section{SIGNATURES}

\vspace{1cm}

\noindent\textbf{BORROWER:}\\
MIDWEST MANUFACTURING CO.\\[1cm]
By: \underline{\hspace{5cm}}\\
Name: Robert Thompson\\
Title: President \& CEO\\
Date: March 1, 2023

\vspace{1cm}

\noindent\textbf{LENDER:}\\
INDUSTRIAL CREDIT PARTNERS, LLC\\[1cm]
By: \underline{\hspace{5cm}}\\
Name: David Morrison\\
Title: Managing Director\\
Date: March 1, 2023

\end{document}
