\documentclass[11pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{times}
\usepackage{fancyhdr}
\usepackage{booktabs}
\usepackage{array}

\pagestyle{fancy}
\fancyhf{}
\rhead{CONFIDENTIAL}
\lhead{Credit Agreement - Sunrise Healthcare Systems}
\rfoot{Page \thepage}

\begin{document}

\begin{center}
{\LARGE\bfseries CREDIT AGREEMENT}\\[0.5cm]
{\large dated as of April 1, 2024}\\[1cm]
{\Large between}\\[0.5cm]
{\Large\bfseries SUNRISE HEALTHCARE SYSTEMS, INC.}\\
{\normalsize (as Borrower)}\\[0.5cm]
{\Large and}\\[0.5cm]
{\Large\bfseries HEALTHCARE FINANCE CORPORATION}\\
{\normalsize (as Administrative Agent and Lender)}\\[1cm]
\rule{0.8\textwidth}{0.4pt}\\[0.5cm]
{\large SENIOR SECURED TERM LOAN FACILITY}\\
{\large \$40,000,000}\\[0.5cm]
\rule{0.8\textwidth}{0.4pt}
\end{center}

\vspace{1cm}

\section{DEFINITIONS}

\textbf{"Borrower"} means Sunrise Healthcare Systems, Inc., a Delaware corporation operating healthcare facilities in the Mid-Atlantic region.

\textbf{"Commitment Amount"} means Forty Million Dollars (\$40,000,000).

\textbf{"EBITDA"} means Net Income plus (a) Interest Expense, (b) income taxes, (c) depreciation, and (d) amortization for any trailing twelve-month period.

\textbf{"EBITDAR"} means EBITDA plus Rent Expense under operating leases.

\textbf{"Leverage Ratio"} means Total Debt divided by EBITDA.

\textbf{"Debt Service Coverage Ratio" or "DSCR"} means (EBITDA minus Capital Expenditures minus Distributions) divided by (Interest Expense plus Scheduled Principal Payments).

\textbf{"Current Ratio"} means Current Assets divided by Current Liabilities.

\textbf{"Maturity Date"} means April 1, 2031.

\section{THE CREDIT FACILITY}

\subsection{Term Loan}
The Lender agrees to make a term loan to the Borrower in the aggregate principal amount of \$40,000,000.

\subsection{Purpose}
Proceeds shall be used for (a) refinancing existing indebtedness, (b) capital expenditures related to facility improvements, and (c) general corporate purposes.

\subsection{Interest Rate}
The Loan shall bear interest at SOFR plus 2.75\%.

\subsection{Amortization}
Principal shall be payable in quarterly installments of \$1,000,000 beginning July 1, 2024.

\subsection{Collateral}
All assets of the Borrower, including but not limited to:
\begin{itemize}
    \item Real property and improvements
    \item Medical equipment and fixtures
    \item Accounts receivable (including Medicare/Medicaid receivables)
    \item Intellectual property and licenses
\end{itemize}

\section{FINANCIAL COVENANTS}

\subsection{Maximum Leverage Ratio}
The Borrower shall maintain a Leverage Ratio not exceeding \textbf{4.00:1.00} at all times.

\subsection{Minimum Debt Service Coverage Ratio}
The Borrower shall maintain a Debt Service Coverage Ratio of not less than \textbf{1.25:1.00}.

\subsection{Minimum EBITDA}
The Borrower shall maintain EBITDA of not less than \textbf{\$10,000,000} for any trailing twelve-month period.

\subsection{Minimum Current Ratio}
The Borrower shall maintain a Current Ratio of not less than \textbf{1.50:1.00}.

\section{REPORTING REQUIREMENTS}

The Borrower shall deliver to the Lender:
\begin{itemize}
    \item Quarterly financial statements within 45 days of quarter-end
    \item Quarterly Compliance Certificate within 45 days of quarter-end
    \item Annual audited financial statements within 90 days of fiscal year-end
    \item Annual operating budget within 30 days of fiscal year start
    \item Copies of all Medicare/Medicaid cost reports
    \item Notice of any material litigation or regulatory action
\end{itemize}

\section{HEALTHCARE-SPECIFIC COVENANTS}

\subsection{Regulatory Compliance}
The Borrower shall maintain all licenses, permits, and certifications required to operate its healthcare facilities.

\subsection{Medicare/Medicaid Participation}
The Borrower shall maintain its participation in Medicare and Medicaid programs in good standing.

\subsection{Professional Liability Insurance}
The Borrower shall maintain professional liability insurance with coverage of not less than \$5,000,000 per occurrence.

\section{EVENTS OF DEFAULT}

The following constitute Events of Default:
\begin{enumerate}
    \item Non-payment of principal or interest within 5 days of due date
    \item Breach of any financial covenant
    \item Material misrepresentation
    \item Cross-default on other indebtedness exceeding \$500,000
    \item Loss of Medicare/Medicaid certification
    \item Material adverse change in business condition
    \item Change of control without consent
\end{enumerate}

\section{REMEDIES}

Upon an Event of Default, Lender may:
\begin{itemize}
    \item Accelerate all outstanding obligations
    \item Increase interest rate by 2.00\%
    \item Exercise remedies against collateral
    \item Require appointment of a receiver
\end{itemize}

\section{SIGNATURES}

\vspace{1cm}

\noindent\textbf{BORROWER:}\\
SUNRISE HEALTHCARE SYSTEMS, INC.\\[1cm]
By: \underline{\hspace{5cm}}\\
Name: Dr. Michael Chen\\
Title: Chief Executive Officer\\
Date: April 1, 2024

\vspace{1cm}

\noindent\textbf{LENDER:}\\
HEALTHCARE FINANCE CORPORATION\\[1cm]
By: \underline{\hspace{5cm}}\\
Name: Jennifer Martinez\\
Title: Senior Vice President, Healthcare Lending\\
Date: April 1, 2024

\end{document}
